\unnumberedSection{Product safety}

\subsection{General safety information}

Read and follow all instructions provided in this manual to ensure safe and correct use of the product.

Keep the product out of the reach of children and pets.  Do not expose the product to extreme temperatures, humidity, or direct sunlight. Use only the recommended accessories and chargers for the product.

If the product shows signs of malfunction, stop using it and contact x-io Technologies using the contact information below.

\subsection{Intended use}

This product is a high-performance, multi-purpose \ac{IMU} designed to accommodate a wide range of data logging and real-time applications. It is intended for use in a variety of applications where motion sensing and data collection are required.

The product must be operated according to the guidelines specified in this manual. It is not intended for use in hazardous or extreme conditions.

\subsection{User responsibilities}

The user is responsible for ensuring that the product is used in accordance with the instructions provided in this manual. The user must ensure that the product is used in a manner that does not cause harm to the product, others, or the environment.

It is the user’s responsibility to regularly inspect the product for any signs of damage or malfunction and to discontinue use if any issues are found. The user must also ensure that the product is disposed of in accordance with local regulations when it reaches the end of its life.

\subsection{Battery safety and handling}

\warning{Incorrect use or storage of batteries can lead to explosions, fire hazards, and personal injury.}

\subsubsection{Charging the battery}

To charge the product, use the provided cable to connect the USB socket on the product to a USB power source.  The product should be supervised at all times while charging. Do not leave it unattended or charge it overnight.

\subsubsection{Battery removal}

The battery is non-removable and should not be removed under any circumstances. Attempting to remove the battery may cause damage or risk injury.

\subsubsection{Battery damage and wear}

\begin{itemize}
    \item Do not use a damaged battery. If you notice any corrosion, dents, bends, leaks, scratches, melting, bubbling, or damage to the plastic cover, the battery should be disposed of immediately.
    \item If a battery has been exposed to water or fire, do not use it. Dispose of it immediately.
    \item If the battery or device becomes unusually hot, or shows signs of wear due to excessive heat (while charging or in use), dispose of it immediately.
    \item If your battery or charger is functioning incorrectly (e.g., not holding charge, LED not functioning, providing more power than usual), dispose of the battery.
\end{itemize}

\subsection{Installation and setup safety}

Avoid placing the product near heat sources or in environments where it may be exposed to moisture, dust, or direct sunlight, as this could affect its performance.

Ensure that the product is securely mounted and positioned to avoid accidental damage. The product must not be exposed to excessive force during installation or operation.

Do not attempt to modify or disassemble the product during installation. If you experience any issues with installation, please contact x-io Technologies using the contact information below.

\subsection{Maintenance and cleaning}

If you are experiencing problems with your product, report this immediately to the x-io Technologies team who will assist you.

Do not attempt to open, modify or repair the product. Alterations to the product and technical modifications are not permitted. Opening or disassembling the product carries a risk of explosion which can cause personal injury.

This product has no consumer serviceable parts.

To clean the product, use a dry, soft cloth. Avoid using abrasive cleaners, solvents, or liquids, as they may damage the product or impair its functionality. Ensure that no moisture enters the device during cleaning.

\subsection{Disposal and environmental considerations}

Do not dispose of this product with household waste. Please return the product to an authorised collection point for recycling. This will help ensure proper disposal and recovery of valuable materials.

The product may contain substances that, if disposed of improperly, could be harmful to the environment or human health. Please follow local regulations for disposal and recycling of electrical and electronic equipment.

\subsection{Compliance and regulatory information}

Users of this product should be aware that regulations for products vary across countries and other administrative regions. For example, different regions will have different rules for what is permitted in terms of radio frequency transmission.

It is the responsibility of the user of this product to ensure that their usage of it complies with the laws and regulations of the relevant local jurisdiction.

The product can be configured for different geographical regions to ensure compliance with local laws.

\subsection{Contact and support information}

The latest documentation and supporting resources for this product can be found on the \productWebPage.

x-io Technologies is the manufacturer and distributor of this product. For other questions, information, technical assistance or ordering instructions, please email us at \href{mailto:info@x-io.co.uk}{info@x-io.co.uk}.
