\section{Overview}

\begin{multicols}{2}

The x-IMU3 is x-io technologies' third generation \ac{IMU}.  It is a high-performance and versatile measurement device designed to accommodate a wide range of data logging and real-time applications including biomechanics, motion-capture, virtual reality, drones, robotics, and industrial.

\acs{USB}, Wi-Fi and Bluetooth provide connectivity for mobile and desktop devices while serial communication supports embedded and industrial systems.  An on-board micro \acs{SD} card allows the x-IMU3 to function as a stand-alone data logger with the ability to download files by USB and Wi-Fi.  Multiple x-IMU3s operating together on the same wireless network will automatically synchronise to stream or log synchronised measurements.

\textbf{Sensors}
\begin{itemize}[nolistsep]
    \item Gyroscope, \textpm{}2000\textdegree{}/s, 400 Hz
    \item Accelerometer, \textpm{}16 g, 400 Hz
    \item Magnetometer, \textpm{}2.5 uT, 20 Hz
    \item High-g accelerometer, \textpm{}200 g, 1600 Hz
    \item Temperature sensor\footnote{The temperature sensor is used for calibration and is not intended to provide an accurate measurement of ambient temperature.}
\end{itemize}

\textbf{Calibration}
\begin{itemize}[nolistsep]
    \item 12-parameter calibration for: axis sensitivity, axis bias, inter-axis misalignment, and package misalignment.
    \item Hard-iron and soft-iron calibration
    \item On-board gyroscope bias correction algorithm
\end{itemize}

\textbf{\acs{AHRS}}
\begin{itemize}[nolistsep]
    \item Algorithm outputs:
    \begin{itemize}
        \item Quaternion
        \item Rotation matrix
        \item Euler angles
        \item Linear acceleration
        \item Earth acceleration
    \end{itemize}
    \item Linear acceleration rejection
    \item Magnetic distortion rejection
    \item 400 Hz update rate
    \item Static accuracy:
        \begin{itemize}
            \item 1\textdegree{} \acs{RMS} inclination
            \item 2\textdegree{} \acs{RMS} heading
        \end{itemize}
\end{itemize}

\columnbreak

\textbf{Communication}
\begin{itemize}[nolistsep]
    \item \acs{USB}
    \item Serial, 3.3V \acs{UART}
    \item \acs{TCP} (Wi-Fi)
    \item \acs{UDP} (Wi-Fi)
    \item Bluetooth (\acs{SPP})
\end{itemize}

\textbf{Wi-Fi}
\begin{itemize}[nolistsep]
    \item Client and \acs{AP} mode
    \item Dual band (2.4 GHz, 5 GHz)
    \item WPA/WPA2-Personal
    \item WPA/WPA2-Enterprise\footnote{WPA/WPA2-Enterprise security is only supported in client mode.} (TBC)
\end{itemize}

\textbf{Data logging}
\begin{itemize}[nolistsep]
    \item Supports \acs{SD} cards up to 32 GB\footnote{The product is supplied with an 8 GB \acs{SD} card that can be upgraded by the user.}
    \item Start/stop logging remotely
    \item USB download
    \item Wi-Fi download
    \item \acs{CSV} output
\end{itemize}

\textbf{Serial accessories}
\begin{itemize}[nolistsep]
    \item Receive data from external sensors and user electronics, e.g. \acs{GPS}, analogue/digital inputs, application-specific sensors.
    \item 3.3 V output to power external electronics
\end{itemize}

\textbf{Battery}
\begin{itemize}[nolistsep]
    \item Internal battery charged by \acs{USB}
    \item 15 hours data logging
    \item 11 hours Bluetooth
    \item 9 hours Wi-Fi client 2.4 GHz
    \item 6 hours Wi-Fi client 5 GHz
\end{itemize}

\textbf{Housing}
\begin{itemize}[nolistsep]
    \item IP67 (TBC)
    \item Wearable strap or chassis mount
\end{itemize}

\textbf{Software \acs{GUI}}
\begin{itemize}[nolistsep]
    \item Real-time data plots and 3D view
    \item Log real-time data to \acs{CSV}
    \item Forward real-time data to other applications
    \item Windows and OSX
\end{itemize}

\textbf{Software \acs{API}}
\begin{itemize}[nolistsep]
    \item Rust, C, C++, Python
    \item Code examples for other languages available
\end{itemize}

\end{multicols}

\clearpage
